### 2023-10-18 main.tex
Bozza 3
Argument correlations

\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}

@@

\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&

@@

\left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right\}\widetilde{H}_{x}

@@

To compute correlations it is enough the above expression. Using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly. We report this explicit formula and the proof in Appendix \ref{appB}.\\
The expression \eqref{SteadyState-coeff-implicit} has two contribution. First a term $\Psi^{'}(\bm{\tau})$ and second a where $b$ of the empty occupations of $\bm{\tau}$ have been replaced by all possible species from $1$ to $N-1$. If the configuration $\bm{\tau}$ has no empty species, this second term vanishes. The existence of the second term is motivated by the fact that, the empty occupation at each site $x$ depend on the other species via $1=\sum_{a=1}^{N}n_{a}^{x}$.\\  

@@

We now consider the second term of the above expression. For any fixed $\ell$ and for any fixed $\bm{\tau}\in \Omega_{\ell}$, $b$ empty occupations are replaced by all possible non-empty species. For a fixed $b$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ with has $\ell<b$, then the this term do not produce any contribution. On the other hand, if $b\geq \ell$ we obtain from $\bm{\tau}$ all possible configuration in the space $ \Omega_{\ell-b}$, where $b$ empties have been replaced by all  species from $1$ to $N-1$. Each of such a configuration is counted $\binom{L-\ell+b}{b}$. By calling $r=\ell-b$ if $b\leq \ell$ we have that 

@@

=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\sum_{\bm{\tau}\in \Omega_{r}}\Psi^{'}(\bm{\tau})\mathbbm{1}_{\{b\leq L-r\}}\dt
As a consequence, we have that the normalization condition reads
\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\mathbbm{1}_{\{b\leq L-\ell\}}=0\dt

@@

\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\mathbbm{1}_{\{b\leq L-\ell\}}=0\dt

@@

The second term on the right hand side in the above equation replaces $b$ empty occupations with all possible non-empty species. If the configuration $\bm{\tau}\in\widehat{\Omega}_{\ell}^{m}$ has $\ell<b$ no contributions are seen. Otherwise, if $\ell\geq b$, $b$ empties are changed, obtaining configuration with $r=\ell-b$ voids occupations, with $r\in \{0,\ldots, L-m-b\}$. Each of such a configuration is counted $\binom{L-r-m}{b}$ times. Therefore, we obtain 

@@

In the second term we exchange the summations obtaining 

@@

Using formula \eqref{ABS} we obtain 

@@

Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,y_{k},c_{k},\ldots,c_{m})$ we have \eqref{exactCorrelations}.

>>>>

\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}

@@

\sum_{\xi_{1}^{u(x)},\ldots,\xi_{a-1},\xi_{a},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&

@@

%\\&=
%\left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right\}\widetilde{H}_{x}

@@

 Using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly, however to compute correlations it is enough the above expression. We report the explicit formula and the proof in Appendix \ref{appB}.\\
In \eqref{SteadyState-coeff-implicit} there are two terms. For every configuration $\bm{\tau}$ the first term just gives $\Psi^{'}(\bm{\tau})$ from formula \eqref{ABS}. The second term acts as follows: for every $b\in\{1,\ldots,L\}$, if $\bm{\tau}$ has more then $b$ empty occupations, it changes $b$ of these empty occupations in all possible species from $1$ to $N-1$ and gives contributions $\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})$ computed in these new configurations with proper coefficients. If $\bm{\tau}$ has less than $b$ empty occupation we do not see any contribution from this second term.\\

@@

We now consider the second term of the above expression. For a fixed $b$, $\ell$ and $\bm{\tau}$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ has $\ell<b$, then this term do not produce any contribution. On the other hand, if $b\geq \ell$ we obtain all possible configuration in the space $ \Omega_{\ell-b}$, where $b$ of the $\ell$ empties have been replaced by all  species from $1$ to $N-1$. Each of such a configuration is counted $\binom{L-\ell+b}{b}$, since we have added,  in all possible ways, $b$ non-empty occupations to the configuration $\bm{\tau}$ that had originally $L-\ell$ sites occupied with non-empty species. By calling $r=\ell-b$ if $b\leq \ell$ we have that 

@@

=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\mathbbm{1}_{\{b\leq L-r\}}\sum_{\bm{\tau}\in \Omega_{r}}\Psi^{'}(\bm{\tau})\dt
As a consequence, by using again the index $\ell$ in the second term, we have that the normalization condition reads
\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt

@@

\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt

@@

In the first summation on the right-hand-side, there is only one term that has all sites empty but the one in position $y_{1},\ldots,y_{m}$ that are occupied by $s_{1},\ldots,s_{m}$. This is reached when $\ell=L-m$ and we denote it by $\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)$. The second term on the right-hand-side in the above equation replaces $b$ empty occupations with all possible non-empty species. If the configuration $\bm{\tau}\in\widehat{\Omega}_{\ell}^{m}$ has $\ell<b$ no contributions are seen. Otherwise, if $\ell\geq b$, $b$ empties are changed, obtaining configuration with $r=\ell-b$ voids occupations, with $r\in \{0,\ldots, L-m-b\}$. Each of such a configuration is counted $\binom{L-r-m}{b}$ times. Therefore, we obtain 

@@

In the second term of the above equation we exchange the summations obtaining 

@@

Using formula \eqref{ABS} we have that 

@@

Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,y_{k},c_{k},\ldots,c_{m})$ we prove \eqref{exactCorrelations}.
